*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-16 Code/Manuscript_O2.Rmd
edits to Acknowledgements & Funding

# Funding
To Be Entered through PLoSONe system and deleted here
Czech Academy of Science visiting fellowship (DAC)
Canada Research Chair in Phytoplankton Ecophysiology (DAC)
Natural Sciences and Engineering Research Council of Canada, 'Latitude and Light' (DAC)
Canada Foundation for Innovation (DAC)
New Brunswick Foundation for Innovation (DAC)
Rice Graduate Fellowship (MS)

>>>>

# Funding
To Be Entered through PLoSONe system and deleted here
Czech Academy of Science visiting fellowship supporting DAC work at AlgaTech (OP)
Canada Research Chair in Phytoplankton Ecophysiology (DAC)
Natural Sciences and Engineering Research Council of Canada, 'Latitude and Light' (DAC)
Canada Foundation for Innovation (DAC)
New Brunswick Foundation for Innovation (DAC)
Rice Graduate Fellowship (MS)
